Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-11-26 src/tex/ms.tex
Update

\usepackage{showyourwork}
\usepackage{amsfonts,amssymb,amsmath}

@@

In contrast, We included the frequency dependence in the modification, which is a first-order approximation of the birefringence model.
This frequency dependence provides stronger enhancement or suppression from the birefringence to high frequency components of the GW, and visa versa. \kw{Redundant.}
Also, \kw{You don't need an also here since you are still talking about the same thing} the frequency dependence can break the degeneracy between $\kappa$ and $\iota$, as this would make the effect of the birefringence affect the amplitude ratio differently compared to $\iota$.
To illustrate the frequency dependence of amplitude birefringence, the observed amplitudes of two polarizations of a simulated GW signal are shown in figure \ref{fig:birefringence}.

@@

% Parameter estimation
The major objective of this study is to constrain GW amplitude birefringence,
which is represented by the opacity parameter $\kappa$. To constrain $\kappa$,
we perform PE with data from the third GW transient catalog \citep{GWTC-2.1,
GWTC-3}, GWTC-3, using Bilby, a Bayesian toolkit for GW data analysis which is
able to calculate posteriors of GW parameters based on interferometer data and
priors for the parameters in question \citep{Bilby}. We set the prior on
$\kappa$ to a uniform distribution between $-1$ and $1$, and perform PE using
the modified waveforms. In both case, we use the same PE configuration as in
\citet{GWTC-2.1, GWTC-3} for each individual events. We also perform test to
check if the PE could recover the PE done by LIGO-Virgo-KAGRA Collaboration
\kw{State that this is a sanity check} (LVK) in \citet{GWTC-2.1, GWTC-3}. We set
the prior on $\kappa$ to be a $\delta$ function at $0$, which is the same as
using GR \kw{This sentence kind of read odd. Add conjunction to link it to the
GR test.}. These control tests result can be found in the data release.
\kw{Link}

>>>>

\usepackage{showyourwork}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{hyperref}

@@

In contrast, We included the frequency dependence in the modification, which is a first-order approximation of the birefringence model.
The frequency dependence can break the degeneracy between $\kappa$ and $\iota$, as this would make the effect of the birefringence affect the amplitude ratio differently compared to $\iota$.
To illustrate the frequency dependence of amplitude birefringence, the observed amplitudes of two polarizations of a simulated GW signal are shown in figure \ref{fig:birefringence}.

@@

% Parameter estimation
The major objective of this study is to constrain GW amplitude birefringence,
which is represented by the opacity parameter $\kappa$. To constrain $\kappa$,
we perform PE with data from the third GW transient catalog \citep{GWTC-2.1,
GWTC-3}, GWTC-3, using Bilby, a Bayesian toolkit for GW data analysis which is
able to calculate posteriors of GW parameters based on interferometer data and
priors for the parameters in question \citep{Bilby}. We set the prior on
$\kappa$ to a uniform distribution between $-1$ and $1$, and perform PE using
the modified waveforms. In both case, we use the same PE configuration as in
\citet{GWTC-2.1, GWTC-3} for each individual events. We also perform test to
check if the PE could recover the PE done by LIGO-Virgo-KAGRA Collaboration
\kw{State that this is a sanity check} (LVK) in \citet{GWTC-2.1, GWTC-3}. We set
the prior on $\kappa$ to be a $\delta$ function at $0$, which is the same as
using GR \kw{This sentence kind of read odd. Add conjunction to link it to the
GR test.}. These control tests result can be found in the \href{https://zenodo.org/record/7338924}{data release}.
